Layered Types -- A structured approach to arbitrarily combine Liquid Types

### 2022-11-14 paper/paper.tex
* Added tests for layer processing to test suite

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{LayeredTypes}
%TODO: Proper Title
%\title[LayeredTypes]{Layered Types -- A structured approach to arbitrarily combine Liquid Types}

@@

In current Liquid Type implementations, types that require multiple predicates are defined as a single type. This may make it difficult for a developer to directly identify which properties a specific liquid type ensures. By separating different properties into a more fine-grained layered approach, this may make it easier to identify these properties. Additionally, by separating the predicates into different layers, it is possible to reuse previously defined liquid types in a more flexible way. For example, if a developer wants to refine a previously defined liquid type, they can now do so by adding a new layer to it, instead of having to redefine the entire type.

@@

@@

Test

@@

@@

\section{Evaluation}
\label{sec:evaluation}
\section{Conclusion}
\label{sec:conclusion}
\section{Acknowledgments}
\label{sec:acknowledgments}

>>>>

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
% \title{LayeredTypes}
%TODO: Proper Title
\title[Layered Types]{Layered Types -- A structured approach to arbitrarily combine Liquid Types}

@@

In current Liquid Type implementations, types that require multiple predicates are defined as a single type. This may make it difficult for a developer to directly identify which properties a specific liquid type ensures. By separating different properties into a more fine-grained layered approach, this may make it easier to identify these properties. Additionally, by separating the predicates into different layers, it is possible to reuse liquid types in a more flexible way. For example, if a developer wants to refine a previously defined liquid type, they can now do so by adding a new layer to it, instead of having to redefine the entire type.

@@

\paragraph{Improved Modularity}

By separating the predicates into different layers, it is possible to reuse previously defined liquid types in a more flexible way. For example, if a developer wants to refine a previously defined liquid type, they can now do so by adding a new layer to it, instead of having to redefine the entire type. Additionally, this also supports the seperation of concerns when collaborating with other developers. In current implementations, when interfacing with other developers' code, one needs to be aware of all the refinements required by such code in order to interact with it. When different properties are divided into proper layers, this is no longer required.

@@

@@

Using this architecture, we provide a flexible framework that allows to easily extend our toy language with various type checking layers. Similar to passes in a compiler, the layers can be added and removed easily. Additionally, the layers can be easily combined to create more complex type checking layers.

@@

\section{Evaluation}
\label{sec:evaluation}
\section{Conclusion}
\label{sec:conclusion}
\section{Acknowledgments}
\label{sec:acknowledgments}
This work was supported by \textit{Fundação para a Ciência e Tecnologia} (FCT) in the LASIGE Research Unit under the ref. UIDB/00408/2020 and UIDP/00408/2020, by the CMU--Portugal project CAMELOT (LISBOA-01-0247-FEDER-045915), and the RAP project under the reference (EXPL/CCI-COM/1306/2021).
